Appendix for: the Forecasting Trap

### 2021-05-19 notebook/model-estimates.Rmd
:construction:

#scale <- 20
x <- siteA$PopulationUntransformed / scale
constants <- list(N = length(siteA$SampleYear),
                  x0 = x[[1]]
)
```

@@

```{r}
#p <- list(r = 2, K = 25, q = 4, b = 2, a = 7) # higher-state peak is optimal

may  <- nimble::nimbleCode({
  x[1] <- x0
  q <- 3
  s <- 2
  r ~ dunif(0,5) #dlnorm(log(1) - s^2/2, s)
  K ~ dunif(0,40) #dlnorm(log(2)- s^2/2, s)
  a ~ dunif(0,5) # dlnorm(log(7) - s^2/2,  s)
  b ~ dunif(1.5,2.5) #dlnorm(log(1) - s^2/2, s)
  sigma ~ dlnorm(log(0.05) - s^2/2, s)

  for(t in 1:(N-1)){
    mu[t] <-  x[t] + x[t] * r * (1 - x[t] / K)  - a * x[t] ^ q / (x[t] ^ q + b ^ q)
    x[t+1] ~ dnorm(log( mu[t] ), sd = sigma)
  }

@@

@@

may_f <- function(x){ # May
      x + x * p$r_mean * (1 - x / p$K_mean)  - (p$a_mean) * x ^ 3 / (x ^ 3 + (p$b_mean) ^ 3)
}

# Matches the optimal policy under these settings (depends on sigma, among others)
logistic_f <- 
  function(x){
      x + x * l_p$r_mean * (1 - x / l_p$K_mean)
  }

states <- seq(0,30, length=200)
landscape <- map_dfr(list(may_f, logistic_f), 
                     function(f) tibble(state = states, f = f(states) -states),
                     .id = "model")

landscape %>% ggplot(aes(state, f, col=model)) + geom_point()
```

>>>>

#scale <- 20
x <- siteA$PopulationUntransformed
constants <- list(N = length(siteA$SampleYear),
                  x0 = x[[1]]
)
```

@@

```{r}
p <- list(r = 2, K = 25, q = 4, b = 2, a = 10)

may  <- nimble::nimbleCode({
  x[1] <- x0
  q <- 4
  r ~ dnorm(2, 0.5)
  K ~ dnorm(25, 8)
  a ~ dnorm(10, 3)
  b ~ dnorm(2, .5)
  sigma ~ dunif(0.0, .1)

  for(t in 1:(N-1)){
    mu[t] <-  x[t] + x[t] * r * (1 - x[t] / K)  - a * x[t] ^ q / (x[t] ^ q + b ^ q)
    x[t+1] ~ dlnorm(log( mu[t] ), sd = sigma)
  }

@@

```{r}
states <- seq(0,30, length=100)
p <- list(r = 2, K = 25, q = 4, b = 2, a = 10)
may_f <- function(y,p){ # May
  p$q <- 4
  pmax(y + y * p$r * (1 - y / p$K)  - p$a * y ^ p$q / (y ^ p$q + p$b ^ p$q), 0)
}

logistic_f <- function(y,p){
    pmax(y + y * p$r * (1 - y / p$K), 0)
}
# draw and plot samples from the mcmc
landscape <- 
  slice_sample(m_draws, n=1000) %>% 
  transpose() %>%
  map_dfr(function(p) 
    map_dfr(list(may_f, logistic_f), 
            function(fun) tibble(state = states, f = fun(states,p)-states),
            .id = "model"),
          .id = "sample")

landscape %>% ggplot(aes(state, f, group=interaction(sample,model), col=model)) + geom_line(alpha=0.01) #+ ylim(c(-5,1))
```

## Approximations

controlling h is actually controlling the bifurcation point directly...

```{r}
landscape <- map_dfr(list(logistic_1, logistic_2, may), 
                     function(f) tibble(state = states, f = f(states, p)),
                     .id = "model")
monkeys <- data.frame(state = x, f = lead(x), model = "data") 
bind_rows(landscape, monkeys) %>% ggplot(aes(state, f, col=model)) + geom_point()
```

@@

apes %>% ggplot(aes(x,x_t1)) + geom_point()
```

### 2021-05-19 notebook/state-tipping-decisions.Rmd
:construction:

---
output: github_document
---

@@

# Matches the optimal policy under these settings (depends on sigma, among others)
logistic_1 <- 
  function(x, h = 0){
    y <- x +  h
    r <- p$r - 0.2

    pmax(
      y + y * r * (1 - y / p$K),  
      0)
  }

logistic_2 <- 
  function(x, h = 0){
    y <- x +  h
    r <- p$r + .5
    pmax(
      y + y * r * (1 - y / p$K),  
      0)
  }
```

@@

landscape <- map_dfr(list(logistic_1, logistic_2, may), 
                     function(f) tibble(state = states, f = f(states, 0) -states),
                     .id = "model")

landscape %>% ggplot(aes(state, f, col=model)) + geom_point()
```

@@

```{r}
matrices <- lapply(list(logistic_1, logistic_2, may), 
       function(f) fisheries_matrices(states, actions, observations, reward_fn, 
                        f, sigma_g, sigma_m, noise = "lognormal")
)
```

```{r, results="hide"}
solns <- lapply(matrices, function(m) mdp_value_iteration(m$transition, m$reward, discount))
```

@@

```{r}
df %>% ggplot(aes(state, action, col=model)) + geom_point(alpha=0.5)

>>>>

---
output: github_document
title: The Forecasting Trap -- notes
---

@@

# Matches the optimal policy under these settings (depends on sigma, among others)
logistic_1 <- 
  function(x, h = 0){
    y = x+h
    pmax(
      y + y * (p$r - .65) * (1 - y / p$K),  
      0)
  }

alt  <- function(x, h = 0, r = .095, K = 20){
  s <- pmax(x - h, 0)
  s + s ^ 2 * r * (1 - s / K)
}

bh <- 
  function(x, h = 0){
    y = x+h
    A <- 1.3 * p$r
    B <- .6 * p$K / (p$r - 1)
    pmax(
      y * A / (1 + y / B),  
      0)
  }
# Matches the optimal policy under these settings (depends on sigma, among others)
logistic <- 
  function(x, h = 0){
    y = x + h
    r <- p$r - .9
    K <- p$K - 4
    pmax(
      y + y * r * (1 - y / K),  
      0)
  }
logistic_2 <- function(x, h = 2) logistic(x,h)
may_2 <- function(x, h = 2) may(x,h)
may_10 <- function(x, h = 10) may(x,h)
```

@@

landscape <- map_dfr(list(logistic_1, alt, may), 
                     function(f) tibble(state = states, f = f(states) -states),
                     .id = "model")

landscape %>% ggplot(aes(state, f, col=model)) + geom_point() + ylim(-5,10) + xlim(0,5)
```

@@

```{r}
matrices <- lapply(list(logistic_1, alt, may), 
       function(f) fisheries_matrices(states, actions, observations, reward_fn, 
                        f, sigma_g, sigma_m, noise = "lognormal")
)
```

```{r, results="hide"}
#solns <- lapply(matrices, function(m) mdp_value_iteration(m$transition, m$reward, discount))
solns <- lapply(matrices, function(m) mdp_policy_iteration(m$transition, m$reward, discount, policy0 = rep(1,length(states)), max_iter = 5000))

@@

```{r}
df %>% ggplot(aes(state, action, col=model)) + geom_line(alpha=0.5)

### 2021-05-19 notebook/tipping_point_appendix.Rmd
:construction:

---
title: 'Appendix'
author: Carl Boettiger
journal: TBD
layout: 3p
bibliography: refs.bib
csl: csl/ecology-letters.csl
#output:
#  tufte::tufte_handout:
#    dev: cairo_pdf
#    latex_engine: xelatex
output: 
  hrbrthemes::ipsum_pdf:
    dev: cairo_pdf
    latex_engine: xelatex

@@

The question of optimal harvest quotas given a population growth model can be posed as a Markov Decision Process (MDP). @Marescot2013 provides an accessible overview of MDP problems and their solutions in conservation context.  @Reed1979 provides a formal proof of optimal harvest strategy for stochastic dynamics under the assumption of any concave growth function. The problem can be summarized as follows:

A manager seeks to maximize the sum of the utility derived from such a harvest
and such a state, $U(X_t,H_t)$, over all time, subject to discount rate $\delta$:

\begin{equation}
\sum_{t=0}^{t=\infty} U(X_t, H_t) \delta^t
\end{equation}

While in principle the utility could reflect many things, including the cost of fishing, market responses to supply and demand, the value of recreational fishing, the intrinsic value fish left in the sea [see @Halpern2013], for simplicity we will assume utility is merely a linear function of the harvest quota set by the manager, i.e. a fixed price $p$ per kilogram of fish harvested: $U(X_t, H_t) = p \min(H_t, X_t)$ (noting that realized harvest cannot exceed the available stock). As units are already specified in dimensionless quantities in this example, so without loss of generality we will set $p=1$.

To solve this optimization, we must also know the dynamics of $X_t$, describing how future stock $X_{t+1}$ changes from the present state, $X_t$, after to harvest $H_t$:

\begin{equation}
X_{t+1} = f(X_t, H_t)
\end{equation}

This problem is already well studied, and it is worth noting that even under the simple utility function which assigns no value to fish that are not harvested, the optimal strategy still seeks to sustain the fish population indefinitely; as @Clark1973 shows for the deterministic function $f$ and @Reed1979 extended to the stochastic case.  As @Reed1979 proves, the optimal strategy can be characterized by a policy of "constant escapement," in which the manager adjusts the harvest effort each year in an effort to ensure the same number or biomass of fish are left in the sea each year.  The optimization problem can then be solved by dynamic programming, using the recursive Bellman equation. This technique, known as stochastic dynamic programming (SDP) is widely used in conservation decision problems [e.g. @Mangel1985, @Marescot2013].

It is worth noting that while constant escapement is used in the management of several important fish stocks such as salmon, most marine fisheries are not managed using this optimal solution for a fluctuating population, but instead rely on a 'constant harvest effort' (or constant "yield") policy.  In the case of a deterministic model at equilibrium, these policies are identical.  Though constant-effort policies are technically sub-optimal for the problem as stated above with stochastic growth, in practice they can be more robust, such as when measurements of the current stock size $X_t$ are uncertain.  These issues are discussed in detail in @pomdp-intro.  For our purposes, it suffices to note that constant escapement policy is relevant both from a theoretical standpoint as the optimal solution for the problem under consideration, and an applied standpoint as a policy that guides management of many salmon fisheries.  The optimal control approach using SDP as illustrated here is used in a wide and growing number of conservation problems.

Bear in mind that in the example presented here, SDP merely serves the role of a convenient and established way for a manager to determine the optimal action, given some model estimation.  Whether we use SDP or some other way to determine the optimal policy, given the model, is immaterial to the conclusion.

@@

To solve the decision problem using SDP, we define the state space and the action space on a discrete grid of 240 points.  The maximum state is set well above the largest carrying capacity used in the models, which limits the influence of boundary effects introduced by the transformation to a discrete, finite grid.  Available harvest actions match the state space, effectively allowing any harvest level to be possible.

```{r model_definitions}
states <- seq(0,24, length.out = 240)
actions <- states
obs <- states
```

The utility (reward) of an action is set to the (realized) harvest (e.g.
a fixed price per unit fish, with no cost applied to harvest effort).  Future
utility is discounted by fixed factor of $0.99$. Classic maximum sustainable 
yield models [@Schaefer1954] ignore discounting, while modern economic optimization
models insist on it, so a small discount conforms to the latter while reasonably
approximating the former.  The qualitative conclusion is not sensitive to the 
discounting rate.

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.99
```

Alternate reward functions with varying price and cost structures are possible but do not qualitatively impact the conclusions.  This reward function is a limiting case of any more complex reward, and corresponds both to classic work that does not model utility explicitly [e.g. MSY theory, @Schaefer1954], as well as explicit assumptions typically made in more recent models [@Reed1979]. Moreover, using a simple reward function makes it clear that model that performs best is not doing so merely because of particular features baked into the a carefully chosen reward rule.

## Ecological Model Definitions

The manager chooses between two different logistic growth models, each of which
can be thought of as an approximation to the underlying "true" population model:

\begin{equation}
f_i(Y) = Y + Y r_i \left( 1 - \frac{Y}{K_i} \right) \xi_i(t)
\end{equation}

where $\xi_i(t)$ is a multiplicative log-normal noise term with mean 1 and log-standard-deviation $\sigma_i$.

Model 1 has $r_1 = 2$, $K = 16$, and $\sigma_1 = 0.05$.
Model 2 has $r_2 = 0.5, K_2 = 10$, and $\sigma_2 = 0.075$.

Meanwhile, the true population growth rate is simulated using a function with
non-linear per-capita growth:

\begin{equation}
f_i(Y) = Y + Y^4 r_i \left( 1 - \frac{Y}{K_i} \right)
\end{equation}

with $r_3 = 0.002$, $K_3 = 10$ and $\sigma_3 = 0.05$.

@@

```{r}
# K is at twice max of f3; 8 * K_3 / 5
f1 <- function(x, h = 0, r = 2, K = 10 * 8 / 5){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}
f2 <- function(x, h = 0, r = 0.5, K = 10){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}

# max is at 4 * K / 5 
f3  <- function(x, h = 0, r = .002, K = 10){
  s <- pmax(x - h, 0)
  s + s ^ 4 * r * (1 - s / K)
}

## gather models together, indicate true model
sigma_g <- 0.05
models <- list("1" = f1, "2" = f2, "3" = f3)
model_sigmas <- c(sigma_g, 1.5 * sigma_g, sigma_g)
true_model <- "3"
```

@@

```{r sdp, results="hide"}
mdp <- memoise::memoise(mdp_value_iteration,
                        cache = memoise::cache_filesystem("cache/"))

policies <- 
  map_dfr(transitions, 
          function(P){
    soln <- mdp(P, reward, discount = discount, 
                epsilon = 0.01, max_iter = 2000, V0 = rep(0,dim(P)[[1]]))
    escapement <- states - actions[soln$policy]
    tibble(states, policy = soln$policy, escapement)
    }, 
  .id = "model")

write_csv(policies, "../data/policies.csv")
```

@@

```{r simulations}
library(mdplearning)
Tmax <- 100
x0 <- which.min(abs(states - 6))
reps <- 100
set.seed(12345)

@@

sims <- 
  map_dfr(names(transitions), 
          function(m){
            policy <- policies %>% filter(model == m) %>% pull(policy)
            map_dfr(1:reps, simulate_policy, policy = policy, .id = "reps")
          },
          .id = "model"
         )

write_csv(sims, "../data/sims.csv")
```

@@

```{r stepahead_unfished}
stepahead_unfished <- sims
stepahead_unfished$state_index <- rep(sims$state_index[sims$model == "1"],3)

stepahead_unfished <- stepahead_unfished  %>% 
  filter(model != "3") %>% 
  mutate(next_state = dplyr::lead(state_index), model = as.integer(model)) %>%
  rowwise() %>%
  mutate(expected = transitions[[model]][state_index, , 1]  %*% states,
         var = transitions[[model]][state_index, , 1]  %*% states ^ 2 - expected ^ 2,
         low = states[max(which(cumsum(transitions[[model]][state_index,,1]) < 0.025)) ],
         high = states[min(which(cumsum(transitions[[model]][state_index,,1]) > 0.975)) ],
         true = states[next_state ]) 
```

@@

stepahead_unfished <- stepahead_unfished %>%
  mutate(sd = sqrt(var),
         score = scoring_fn(expected, true, sd))

@@

```{r}
predictions <- 
  stepahead_unfished %>% 
  select(time, model, reps, expected, low, high, true, score) %>% 
  mutate(scenario = "A_unfished") %>% 
  bind_rows(stepahead_fished  %>% 
          select(time, model, reps, expected, low, high, true, score) %>% 
          mutate(scenario = "B_fished")
  ) %>% 
  mutate(model = as.character(model))

write_csv(predictions, "../data/predictions.csv")
```

@@

```{r plot_npv}
##  Net Present Value accumulates over time
npv_df <- sims %>% 
  group_by(model, reps) %>%
  mutate(npv = cumsum(value * discount ^ time)) %>%
  group_by(time, model)  %>% 
  summarise(mean_npv = mean(npv), .groups="drop") %>% 
  arrange(model, time)

write_csv(npv_df, "../data/npv_df.csv")
```

@@

```{r}
am <- am1$df %>%
  mutate(belief = am1$posterior$V1,
         method = "learning") %>%
  bind_rows(non_am) %>%
  mutate(stock = states[state],
         quota = actions[action]) %>%
  select(time, stock, quota, belief, method)

write_csv(am, "../data/am.csv")

@@

## Adaptive management over many models

We repeat the analysis above over a grid of $r$ and $K$ values.

```{r}
# compare over grid set of candidate r and K
rs <- c(0.01, 0.1, 0.2, 0.3, 0.4, 0.5, 2)
Ks <- c(0.5, 1, 1.5, 4, 10, 16)
sigma <- 0.1
n_models <- length(rs)*length(Ks)
pars <- expand.grid(rs, Ks)
names(pars) <- c("r", "K")
pars$sigma <- 0.1
closure <- function(r, K){
  function(x, h = 0){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
  }
}
many_models <-  lapply(1:n_models, function(i) closure(pars[i,"r"], pars[i,"K"]))

# transition matrices
many_transitions <- lapply(seq_along(many_models), function(i) 
  transition_matrices(many_models[[i]], states,  actions, sigma))
names(many_transitions) <- as.character(seq_along(many_models))
true_transition <- transition_matrices(f3, states, actions, sigma_g)

## Once again, initial belief favors "model 1"
model_prior <- c(rep(.01, n_models-1) / (n_models - 1), .99)

With the transition matrices defined for all `r n_models` models, we perform adaptive management as before:

```{r}
adaptive_management <- memoise::memoise(mdp_learning, cache = memoise::cache_filesystem("cache/"))
am_many <- adaptive_management(many_transitions,  
                               reward = reward, 
                               discount = discount,
                               model_prior = model_prior,
                               x0 = x0, 
                               Tmax = 20, 
                               true_transition = true_transition, 
                               epsilon = 0.001, 
                               max_iter = 2000)

As before, we can compare the adaptive learning case to the policy which accounts for the initial uncertainty over all `r n_models` models, but does not seek to learn.

```{r}
policy_many <- policy_planning(many_transitions, reward = reward,  discount = discount,
                          model_prior = model_prior, Tmax = 20, 
                          epsilon = 0.001, max_iter = 2000)

non_am_many <- mdp_planning(true_transition,  
                       reward = reward, 
                       discount = discount,
                       model_prior = model_prior,
                       x0 = x0, 
                       a0 = 1,
                       policy = policy_many$policy,
                       Tmax = 20) %>% 
  mutate(belief = 0.99, # belief in model 1 is fixed
         method = "planning")
```

Again we record the posterior belief in the 'model 1' parameter values, and stack the data frames for learning and planning-only cases into a single file used to generate figure 3B.

```{r}
model1 <- dim(am_many$posterior)[2]
am_multi <- am_many$df %>% 
  mutate(belief = am_many$posterior[,model1],
         method = "learning") %>%
  bind_rows(non_am_many) %>%
  mutate(stock = states[state],
         quota = actions[action]) %>%
  select(time, belief, stock, quota, method)

write_csv(am_multi, "../data/am_multi.csv")
```

## Posteriors

With `r n_models` possible models instead of two, the probability weight (belief) in Model 1 does not fully capture the evolution of the belief probabilities over time.
To better illustrate how these beliefs evolve over the course of the simulation, I plot the marginal probabilities over values of $r$ and $K$ across the models over time.
Note that Model 1 values, $r = 2$, $K = 16$, are quickly disfavored.

```{r}
posteriors <- 
  data.frame(model = as.character(1:n_models), t(am_many$posterior)) %>%
  left_join(mutate(pars, model = as.character(1:n_models))) %>%
  pivot_longer(starts_with("X"), 
               values_to = "probability",
               names_to = "time") %>% 
  mutate(time = as.integer(as.factor(time)))

r_marginals <- posteriors %>% 
  group_by(time,r) %>% 
  summarise(prob = sum(probability), .groups = "drop")

K_marginals <- posteriors %>% group_by(time,K) %>% 
  summarise(prob = sum(probability), .groups = "drop")
```

From the table of marginal probabilities, we generate the corresponding plots

```{r fig.width=8, fig.height=4, fig.cap = "Fig S1: Marginal probabilities of parameters $r$ and $K$ over the course of adaptive management over all 42 models." }
belief_r <- r_marginals %>% 
  mutate(r = as.character(r)) %>%
  ggplot(aes(time, prob, group = r, col = r)) + geom_line() +
  geom_point()

belief_K <- K_marginals %>% 
  mutate(K = as.character(K)) %>%
  ggplot(aes(time, prob, group = K, col = K)) + geom_line() +
  geom_point()

belief_r + belief_K 
```

For most of the simulation, the most probable $r$ value is around 0.3, and the most probable $K$ value around 1.5.

@@

write_csv(model_curves, "../data/model_curves.csv")

@@

The resulting model curves are shown in the main paper, Fig 4A.

## Growth models in the many-models case

The corresponding figure for the case of `r n_models` models.

```{r plot_many_models, fig.width=7, fig.height=5, fig.cap="growth curves for 42 candidate models, shaded by belief at timestep 20, relative to the true model.  The curve with parameter values corresponding to 'model 1' are recognized in the highest arc, with belief weight of less than 1%."}

final_belief <- posteriors %>% filter(time == max(time)) %>%
  select(model, belief = probability) %>% mutate(type = "candidate") %>%
  bind_rows(data.frame(belief = 1, model="true", type="true"))

model_set <-c(f3,  many_models)
names(model_set) <- c("true", 1:length(many_models))
d <- 
  map_dfc(model_set, function(f) f(states) - states) %>%
  mutate(state = states) %>% pivot_longer(names(model_set), "model") %>%
  left_join(final_belief)

d %>% 
  ggplot(aes(state, value, group=model, col = type, alpha = belief)) +
  geom_line(lwd=1) + 
  coord_cartesian(ylim = c(-5, 8), xlim = c(0,16)) +
  ylab(bquote(f(x) - x)) + xlab("x")
```

>>>>

---
title: 'Appendix for: the Forecasting Trap'
author: Carl Boettiger
journal: TBD
layout: 3p
bibliography: refs.bib
csl: csl/ecology-letters.csl
#output:
#  tufte::tufte_handout:
#    dev: cairo_pdf
#    latex_engine: xelatex
output: 
  hrbrthemes::ipsum_pdf:
    dev: cairo_pdf
    latex_engine: xelatex

@@

@@

```{r model_definitions}
states <- seq(0,30, length=100)
actions <- seq(0,30, length.out = 100)
obs <- states
```

```{r}

benefit <- 1
cost <- 1 # quadratic costs
reward_fn <- function(x,h) benefit * x - (h ^ cost)
discount <- 0.999
```

@@

```{r}

p <- list(r = 2, K = 25, q = 4, b = 2, a = 7) # higher-state peak is optimal

# Matches the optimal policy under these settings (depends on sigma, among others)
f1 <- 
  function(x, h = 0){
    y = x+h
    pmax(
      y + y * (p$r - .65) * (1 - y / p$K),  
      0)
  }

f2  <- function(x, h = 0, r = .095, K = 20){
  s <- pmax(x - h, 0)
  s + s ^ 2 * r * (1 - s / K)
}

f3 <- 
  function(x, h = 0){ # May
    y <- x +  h
    pmax(
      ## controlling h is controlling the bifurcation point directly...
      y + y * p$r * (1 - y / p$K)  - p$a * y ^ p$q / (y ^ p$q + p$b ^ p$q),  
      0)
  }

## gather models together, indicate true model
sigma_g <- 0.05
models <- list("1" = f1, "2" = f2, "3" = f3)
model_sigmas <- c(sigma_g, sigma_g, sigma_g)
true_model <- "3"
```

@@

```{r sdp, results="hide"}
mdp <- memoise::memoise(mdp_policy_iteration,
                        cache = memoise::cache_filesystem("cache/"))

policies <-
  map_dfr(transitions, 
          function(P){
    soln <- mdp(P, reward, discount = discount, max_iter = 5000, policy0 = rep(1, length(states)))
    tibble(states, policy = soln$policy, actions = actions[soln$policy])
    }, 
  .id = "model") 
```

@@

```{r simulations}
library(mdplearning)
Tmax <- 100
x0 <- which.min(abs(states - 1.5))
reps <- 100
set.seed(12345)

@@

sims <- 
  map_dfr(names(transitions), 
          function(m){
            policy <- policies %>% filter(model == m) %>% pull(policy)
            map_dfr(1:reps, simulate_policy, policy = policy, .id = "reps")
          },
          .id = "model"
         )
```

```{r}
## add predictions from each model.  
do_nothing <- rep(1, length(states))
unmanaged <- mdp_planning(transitions[[true_model]], reward, discount,
           policy = do_nothing, x0 = x0, Tmax = Tmax) %>%
    select(value, state_index = state, time, action_index = action)  %>% 
    mutate(state = states[state_index])

@@

@@

@@

```{r}
predictions <- 
  stepahead_fished  %>% 
  select(time, model, reps, expected, low, high, true, score)  %>% 
  mutate(model = as.character(model))

```{r}

fig1cd <- predictions %>%
  ggplot(aes(x = score, group = model, fill = model)) +
  geom_histogram(binwidth = 2, show.legend = FALSE) +
  coord_cartesian(xlim = c(-100, 1), ylim = c(0,4000)) +
  xlab("Proper score") +
  facet_wrap(~scenario, ncol = 1, labeller =as_labeller(c(
    A_unfished = "C.",
    B_fished = "D."))) + 
  scale_x_continuous(breaks = c(-100, 0)) +
  theme(axis.text.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        )

fig1ab <- predictions %>% 
  filter(reps == "2", time < 10) %>%
  ggplot(aes(time, col = model, fill = model)) + 
  geom_point(aes(y = expected)) + 
  geom_errorbar(aes(ymin = low, ymax = high)) +
  geom_point(aes(y = true), pch = "*", size = 12, 
             alpha = 0.6) +
  ylab("stock size")

fig1ab + fig1cd + 
  plot_layout(widths = c(3,1), guides = 'collect') + 
  theme(plot.margin = margin(0, 0, .1, .1, "cm"))
```

@@

```{r plot_npv}
##  Net Present Value accumulates over time
npv_df <- sims %>% 
  group_by(model, reps) %>%
  mutate(npv = cumsum(value * discount ^ time)) %>%
  group_by(time, model)  %>% 
  summarise(mean_npv = mean(npv), .groups="drop") %>% 
  arrange(model, time)
```

```{r figure2, message = FALSE, fig.cap = "Ecological and economic performance of each forecast."}
plot_ecology <- 
  sims %>%
  mutate(model = as.character(model), resp = as.character(reps)) %>%
  group_by(model, time) %>%
  summarise(mean_state = mean(state), sd = sd(state), .groups = "drop") %>%
  filter(time < 25, model != "3") %>%
  ggplot(aes(time, mean_state)) + 
  geom_line(aes(col = model), lwd=1.5, show.legend = FALSE) +
  geom_ribbon(aes(ymin = mean_state - 2*sd, 
                    ymax = mean_state + 2*sd,
                    fill = model),
                alpha = 0.2, show.legend = FALSE) +
  ylab("state") + 
  labs(subtitle = "A. Ecological outcomes")

optimal <- select(filter(npv_df, model == "3"), time, mean_npv)

plot_econ <- 
npv_df %>%
  mutate(model = as.character(model), resp = as.character(reps)) %>%
  filter(model != "3", time %in% seq(1,100, by = 5)) %>%
  ggplot(aes(time, mean_npv)) +
  geom_line(data = optimal, lwd = 1.5, col = "grey20") +
  geom_point(aes(col=model), size = 4, alpha = 0.8) + 
  ylab("Net present value") + xlab("time") + 
  labs(subtitle = "B. Economic outcomes")

plot_ecology + plot_econ
```

@@

```{r}
am <- am1$df %>%
  mutate(belief = am1$posterior$V1,
         method = "learning") %>%
  bind_rows(non_am) %>%
  mutate(stock = states[state],
         quota = actions[action]) %>%
  select(time, stock, quota, belief, method) 
```

@@

@@

@@

```{r}
plot_models <- 
  model_curves %>% 
  ggplot(aes(state, value, col=model, lty=model)) +
  geom_hline(aes(yintercept = 0)) + 
  geom_line(show.legend = FALSE) + 
  coord_cartesian(ylim = c(-5, 8)) +
  ylab(bquote(f(x) - x)) + xlab("x")

plot_policies <- policies %>%
  ggplot(aes(states, actions, col=model, lty=model)) + 
  geom_line() + xlab("state")

plot_models + labs(subtitle="A") + plot_policies + labs(subtitle="B")
```

```{r}
```
